Evidence accumulation modelling offers new insights into the cognitive mechanisms that underlie linguistic and action-based training

### 2024-12-09 manuscript/supplementary/supplementary.Rmd
updated formula text spacing

<!-- the below two lines directly change the default Figure and Table naming to Supplementary -->
<!-- see here for more details - https://stackoverflow.com/questions/47173279/internationalization-r-knitr-figure-caption-label -->

>>>>

<!-- the below two lines directly change the default Figure and Table naming to Supplementary -->

<!-- see here for more details - https://stackoverflow.com/questions/47173279/internationalization-r-knitr-figure-caption-label -->
